---
title: "Weight of Fish"
author: "MarenaO"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

### Best Models

<<<<<<< HEAD
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

According to this information, the best two regressor model is the one that uses Height and width. It is also the best model overall since it has the highest adjusted r-squared value of 0.94.

### Best Two regressor model

The best two regressor model is the one that uses height and weight.

## Pike

```{r}
Pike<- filter(Fish, Species == "Pike")
Pike = subset(Pike, select = -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

According to this plot, the best two regressor model is the one that uses Length 1 and Length 3. It's adjusted r-squared value is around 0.965. Although, it is not the best model overall since it does not have the highest adjusted r-squared value.

## Roach

```{r}
Roach<- filter(Fish, Species == "Roach")
Roach = subset(Roach, select = -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomleft",main="Adjusted R^2")
```

### Best Two regressor model

According to this plot, the best two regressor model is the one that uses Length 3 and width. It's adjusted r-squared value is a little above 0.845. It is also the best model overall since it has the highest adjusted r-squared value.


## Final Summary Statements

I took a while completing this assignment because I was unfamiliar on how to do certain things leading up to the problem. For example, I forgot how to read in the data, as well as filter out a specific dataset. Although, once I found the commands for this, the rest of the assignment went quite well. I was able to find the best 2 regressor models for a Perch, a Roach, and a Pike. For the perch, I found that the best two regressor model is the one that uses Height and width. It was also the best model overall. For the pike, the best two regressor model is the one that uses Length 1 and Length 3. For the roach, the best two regressor model is the one that uses Length 3 and width. It was also the best model overall. So, for the roach and the perch, the 2 regressor models also happened to be the best models overall since they had the highest adjusted r-squared value.