---
title: "Weight of Fish"
author: "MarenaO"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

### Best Models

<<<<<<< HEAD
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

According to this information, the best two regressor model is the one that uses Height and width. It is also the best model overall since it has the highest adjusted r-squared value of 0.94.

=======
>>>>>>> parent of 7d91fb4... comment on best moel for perch
### Best Two regressor model

The best two regressor model is the one that uses height and weight.

## Pike

```{r}
Pike<- filter(Fish, Species == "Pike")
Pike = subset(Pike, select = -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

According to this plot, the best two regressor model is the one that uses Length 1 and Length 3. It's adjusted r-squared value is around 0.965. Although, it is not the best model overall since it does not have the highest adjusted r-squared value.

## Roach

```{r}
Roach<- filter(Fish, Species == "Roach")
Roach = subset(Roach, select = -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2", legend="bottomleft",main="Adjusted R^2")
```

### Best Two regressor model

According to this plot, the best two regressor model is the one that uses Length 3 and width. It's adjusted r-squared value is a little above 0.845. It is also the best model overall since it has the highest adjusted r-squared value.


## Final Summary Statements